\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2015-11-24 doc/USER_MANUAL/copyright_and_version.tex
updates manual, makes latex header more similar in all specfem versions; add a sentence about contributions and copyrights

\addcontentsline{toc}{chapter}{Copyright}

@@

\chapter*{Copyright}

@@

Princeton University, USA, and CNRS / University of Marseille, France

$\copyright$ Princeton University and CNRS / University of Marseille, July 2012

This program is free software; you can redistribute it and/or modify
it under the terms of the GNU General Public License as published
by the Free Software Foundation (see Appendix \ref{cha:License}).\\

\textbf{\underline{Evolution of the code:}}\\

>>>>

@@

\chapter*{Copyright}
\addcontentsline{toc}{chapter}{Copyright}

@@

Princeton University, USA, and CNRS / University of Marseille, France\\
$\copyright$ Princeton University and CNRS / University of Marseille, July 2012\\

\noindent
This program is free software; you can redistribute it and/or modify
it under the terms of the GNU General Public License as published
by the Free Software Foundation (see Appendix \ref{cha:License}).\\

\noindent
Please note that by contributing to this code, the developer understands and agrees that this project and contribution
are public and fall under the open source license mentioned above.\\

\noindent
\textbf{\underline{Evolution of the code:}}\\

### 2015-11-24 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
added a sentence about varying density in fluids to the users manual
updates manual, makes latex header more similar in all specfem versions; add a sentence about contributions and copyrights

% !TEX encoding = IsoLatin
%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[oneside,english]{book}
\usepackage[T1]{fontenc}
%% DK DK we do not accept accented letters, use the old LaTeX syntax
%% DK DK for them instead: \'e \`e  \"e \^e and so on.
%% DK DK \usepackage[latin1]{inputenc}
\usepackage[letterpaper]{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\usepackage{babel}
\usepackage{float}
\usepackage{textcomp}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[authoryear]{natbib}
\usepackage[unicode=true,pdfusetitle,
 bookmarks=true,bookmarksnumbered=true,bookmarksopen=false,
 breaklinks=false,pdfborder={0 0 0},backref=section,colorlinks=false,pdfpagemode=None]
 {hyperref}
\hypersetup{
 pdftex,pdfstartview=FitH,pdfpagelayout=SinglePage}
\usepackage{breakurl}

@@

% figures
%\usepackage[dvips]{epsfig}

% hyperlinks to sections and references

\newcommand{\urlwithparentheses}[1]{(\url{#1})}

% biblio GJI
\bibliographystyle{abbrvnat}

@@

% colors for the text
\@ifundefined{definecolor}
 {\usepackage{color}}{}
\newcommand{\red}[1]{\textcolor{Red}{#1}}

@@

\usepackage{babel}

@@

@@

\date{\today}

@@

\addcontentsline{toc}{chapter}{References} \bibliography{bibliography}

@@

>>>>

% !TEX encoding = IsoLatin
%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[oneside,english]{book}
\usepackage[T1]{fontenc}
%% DK DK we do not accept accented letters, use the old LaTeX syntax
%% DK DK for them instead: \'e \`e  \"e \^e and so on.
%% DK DK \usepackage[latin1]{inputenc}
\usepackage[letterpaper]{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}

% table of contents and numbering
\usepackage{tocbibind}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}

\usepackage{babel}
\usepackage{float}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{amssymb}

\IfFileExists{url.sty}{\usepackage{url}}
                      {\newcommand{\url}{\texttt}}

% biblio
\usepackage[authoryear]{natbib}
% biblio GJI
\bibliographystyle{abbrvnat}

% figures
\usepackage{graphicx}

% we are running pdflatex, so convert .eps files to .pdf
%\usepackage[dvips]{epsfig}

% colors to show the corrections
\usepackage[dvipsnames,usenames]{xcolor}
\definecolor{light-gray}{rgb}{0.7,0.7,0.7}
\definecolor{dark-gray}{rgb}{0.1,0.1,0.3}
\definecolor{light-blue}{rgb}{0.7,0.7,0.9}
\definecolor{dark-blue}{rgb}{0.2,0.2,0.5}

% hyperlinks to sections and references
\usepackage[pdftex]{hyperref}
% more options
\hypersetup{
  bookmarks=true,
  bookmarksnumbered=true,
  pdfpagemode=UseNone,
  pdfstartview=FitH,
  pdfpagelayout=SinglePage,
  pdfborder={0 0 0},
  colorlinks=true,      % color links
  citecolor=dark-gray,  % citation links
  filecolor=dark-gray,  % file links
  linkcolor=dark-gray,  % internal link (rgb values)
  urlcolor=dark-blue    % external weblinks
}

% create thumbnails
%\usepackage[pdftex]{thumbpdf}

\usepackage{breakurl}

@@

% hyperlinks to sections and references
\newcommand{\urlwithparentheses}[1]{(\url{#1})}

@@

% colors for the text
\newcommand{\red}[1]{\textbf{\textcolor{Red}{#1}}}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Start of document.

@@

% date of last edit
\date{\today}

@@

\bibliography{bibliography}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
